Framing Effects in the Wild

### 2022-09-02 pres/Presentation.Rmd
Update presentation

TreatmentTrendPlot(size = 2, 
                   cntrl_col = "#004A95", 
                   treat_col = "#cc0000") +
  theme_xaringan()

@@

EffectPlot(multi = F, scaled = "raw", size = 2) +
  theme_xaringan()

@@

EffectPlot(multi = T, scaled = T, size = 2) +
  theme_xaringan()

@@

EffectByWavePlot(size = 2) +
  theme_xaringan()

@@

EffectByWavePlot("2880h_clean", size = 2) +
  theme_xaringan()

@@

EffectByWavePlot(dv = "1210_clean", size = 2) +
  theme_xaringan()

@@

EffectByWavePlot(dv = "430i_clean", size = 2) +
  theme_xaringan()

@@

EffectByWavePlot(dv = "mip_mig", size = 2) +
  theme_xaringan()

>>>>

TreatmentTrendPlot(size = 2, 
                   dpa_corrected = T) +
  theme_xaringan()

@@

DiDPlot(multi = F, scaled = "raw", size = 2) +
  theme_xaringan()

@@

DiDPlot(multi = T, scaled = T, size = 2) +
  theme_xaringan()

@@

DiDByWavePlot(size = 2) +
  theme_xaringan()

@@

DiDByWavePlot("2880h_clean", size = 2) +
  theme_xaringan()

@@

DiDByWavePlot(dv = "1210_clean", size = 2) +
  theme_xaringan()

@@

DiDByWavePlot(dv = "430i_clean", size = 2) +
  theme_xaringan()

@@

DiDByWavePlot(dv = "mip_mig", size = 2) +
  theme_xaringan()
